---
title: "PrelimRSA"
author: "AC"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8)
```

```{r loadPackages, message = FALSE, echo = FALSE, warning = FALSE}
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(Rmisc)
library(lme4)
library(lmerTest)
library(sjPlot)
library(car)
```

```{r plottingVars, echo = FALSE}
# Define plot theme
rsa_theme <- theme(title = element_text(size = 26, vjust = 2, face = "bold"),
        axis.title.x = element_text(size = 26),
        axis.title.y = element_text(size = 26, vjust = 1.5),
        axis.text.x = element_text(size = 24, colour = "black", vjust = 0.6),
        axis.text.y = element_text(size = 24, colour = "black"),
        legend.title = element_text(size = 24),
        legend.text = element_text(size = 24),
        legend.position = "bottom",
        strip.text = element_text(size = 24, face = "bold"), # Text in strip headings
        panel.grid.major = element_blank(), # Remove grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
```

```{r loadData, echo = FALSE}
# Read in behavioral data and change variable types
behavdata = read.csv("data/MotERBehavdata_remembered.csv")
behavdata$subid = as.factor(behavdata$subid)
behavdata$HighRewardStim = ifelse(as.numeric(as.character(behavdata$subid)) %% 2 == 0, "High Reward Cat - Face","High Reward Cat - Place")

# Read in demographic data and change variable types
demog = read.csv("data/MotERdemog.csv")
demog$subid = as.factor(demog$subid)
demog$Gender = as.factor(demog$Gender)

# Merge behavioral and demographic data
behavdata <- full_join(behavdata, demog, by = "subid")

# Replace numeric AgeGroup column with factor AgeGroup column
behavdata <- behavdata %>% select(-AgeGroup)
behavdata$AgeGroup = ifelse(behavdata$ExactAge < 13, "Kid",ifelse(behavdata$ExactAge >= 18, "Adult", "Teen"))
behavdata$AgeGroup <- factor(behavdata$AgeGroup, levels = c("Kid", "Teen", "Adult"))

# Average across retrieved and not retrieved measures (for plotting)
behavdata$HighRewAssocHitDay2all <- (behavdata$HighRewAssocHitDay2 + behavdata$HighRewAssocRetrievedHitDay2) / 2
behavdata$LowRewAssocHitDay2all <- (behavdata$LowRewAssocHitDay2 + behavdata$LowRewAssocRetrievedHitDay2) / 2
```

```{r wrangleDataBehav, echo = FALSE}
# Melt data for stats and plots ---

# Day 2 specific associative memory
assochitd2.long = melt(behavdata,
                       id.vars = c("subid", "HighRewardStim", "AgeGroup", "ExactAge", "Gender"),
                       measure.vars = c("HighRewAssocHitDay2", "LowRewAssocHitDay2", 
                                        "HighRewAssocRetrievedHitDay2", "LowRewAssocRetrievedHitDay2"),
                       variable.name = "assoc")
names(assochitd2.long)[names(assochitd2.long) == "value"] <- "mem"

# Code RewardType
findRew <- "(High|Low)"
assochitd2.long <- transform(assochitd2.long, RewardType = stringr::str_extract(assoc, findRew))

# Code RetCond
findRet <- "(Retrieved)"
assochitd2.long <- transform(assochitd2.long, RetCond = stringr::str_extract(assoc, findRet))
assochitd2.long$RetCond[is.na(assochitd2.long$RetCond)] <- "NotRetrieved"
assochitd2.long$RetCond <- as.factor(assochitd2.long$RetCond)

# Day 2 specific associative memory averaged (for plotting)
assochitd2all.long = melt(behavdata,
                          id.vars = c("subid", "HighRewardStim", "AgeGroup", "ExactAge", "Gender"),
                          measure.vars = c("HighRewAssocHitDay2all", "LowRewAssocHitDay2all"),
                          variable.name = "assoc")
names(assochitd2all.long)[names(assochitd2all.long) == "value"] <- "mem"
assochitd2all.long <- transform(assochitd2all.long, RewardType=stringr::str_extract(assoc, findRew))
```

# Memory Performance

## Specific source memory increased for high reward memoranda after 24 hrs across all ages

0. Linear age model is best-fitting
1. Main effects of reward level (p < 0.001) and retrieval condition (p < 0.001)

```{r analyzeBehav, echo = FALSE, warning = FALSE, message = FALSE}
# Z-score age and add age squared
assochitd2.long$ageScaled <- scale(assochitd2.long$ExactAge) # Scale age
assochitd2.long$ageScaledsq <- (assochitd2.long$ageScaled)^2 

# Make high reward category into a factor
assochitd2.long$HighRewardStim <- as.factor(assochitd2.long$HighRewardStim)
assochitd2.long$RewardType <- as.factor(assochitd2.long$RewardType)

# Find best-fitting age model
assocmemmodelagelin <- lmer(mem ~ RewardType * RetCond * ageScaled + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = assochitd2.long) 
assocmemmodelagesq <- lmer(mem ~ RewardType * RetCond * ageScaled + RewardType * RetCond* ageScaledsq + HighRewardStim +  (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = assochitd2.long) 
anova(assocmemmodelagelin,assocmemmodelagesq) # agelin preferred

# Find viable rfx structure
# assocmemmodelfullrfx <- lmer(mem ~ RewardType * RetCond * ageScaled + HighRewardStim + (RewardType*RetCond||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", RetCond = "contr.sum", HighRewardStim = "contr.sum"), data = assochitd2.long) # not identifiable
# assocmemmodelrewardrfx <- lmer(mem ~ RewardType * RetCond * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", RetCond = "contr.sum", HighRewardStim = "contr.sum"), data = assochitd2.long)  # not identifiable
assocmemmodelretrfx <- lmer(mem ~ RewardType * RetCond * ageScaled + HighRewardStim + (RetCond||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", RetCond = "contr.sum", HighRewardStim = "contr.sum"), data = assochitd2.long) 

# Model stats
Anova(assocmemmodelretrfx, type = "III")
# effectsize::standardize_parameters(assocmemmodelretrfx)

# Plot
ggplot(assochitd2all.long, aes(y = mem, x = ExactAge, colour = RewardType, group = RewardType)) +
  geom_point(size = 3) + 
  stat_smooth(method = "lm", aes(fill = RewardType), size = 3) + # add line of best fit
  xlab("Age") + # x axis label
  ylab("Specific Source Memory Day 2") + # y axis label
  scale_colour_manual(labels = c("high","low"), values = c("gold", "snow4"), name = "Reward Level") +
  scale_fill_manual(labels = c("high","low"), values = c("gold", "snow4"), guide = "none") +
  geom_line(aes(group = subid), color = "grey", size = .1) +
  ylim(0, 0.602) +
  rsa_theme
ggsave('figures/spec_source_mem_day2.png', width = 12, height = 8)
```

# VTC Pattern Similarity

```{r wrangleDataVTCPatternSim, echo = FALSE}
# Read in ERS data and change variable types
VTCRSAdata = read.csv("data/RSAdata_VTC.csv")
VTCRSAdata$subid = as.factor(VTCRSAdata$subid)

# Merge ERS and demographic data
VTCRSAdata <- full_join(VTCRSAdata, demog, by = "subid")
VTCRSAdata$HighRewardStim = ifelse(as.numeric(as.character(VTCRSAdata$subid)) %% 2 == 0, "High Reward Cat - Face","High Reward Cat - Place")

# Read in mask voxel numbers and change variable types
VTCERSvoxels = read.csv("data/RSAdfQAVTC.csv")
VTCERSvoxels$subID = gsub("sub-", "", VTCERSvoxels$subID)
VTCERSvoxels$subid = as.factor(VTCERSvoxels$subID)

# Merge ERS and voxel data
VTCRSAdata <- full_join(VTCRSAdata, VTCERSvoxels, by = "subid")

# Melt data for stats and plots ---

# VTC ERS
VTCers.long = melt(VTCRSAdata,
                   id.vars = c("subid", "HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldencvoxnum"),
                   measure.vars = c("highrewardERS", "lowrewardERS"),
                   variable.name = "ERScond")
names(VTCers.long)[names(VTCers.long) == "value"] <- "similarity"
findRew <- "(high|low)"
VTCers.long <- transform(VTCers.long, RewardType=stringr::str_extract(ERScond, findRew))
VTCers.longwstat = summarySE(VTCers.long, measurevar = "similarity", groupvars = c("RewardType", "AgeGroup"))

# VTC encoding similarity
VTCencsim.long = melt(VTCRSAdata,
                      id.vars = c("subid", "HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldencvoxnum"),
                      measure.vars = c("highrewardencsim", "lowrewardencsim"),
                      variable.name = "encsimcond")
names(VTCencsim.long)[names(VTCencsim.long) == "value"] <- "similarity"
findRew <- "(high|low)"
VTCencsim.long <- transform(VTCencsim.long, RewardType=stringr::str_extract(encsimcond, findRew))
VTCencsim.longwstat = summarySE(VTCencsim.long, measurevar = "similarity", groupvars = c("RewardType", "AgeGroup"))

# VTC retrieval similarity
VTCretsim.long = melt(VTCRSAdata,
                      id.vars = c("subid", "HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldencvoxnum"),
                      measure.vars = c("highrewardretsim", "lowrewardretsim"),
                      variable.name = "retsimcond")
names(VTCretsim.long)[names(VTCretsim.long) == "value"] <- "similarity"
findRew <- "(high|low)"
VTCretsim.long <- transform(VTCretsim.long, RewardType=stringr::str_extract(retsimcond, findRew))
VTCretsim.longwstat = summarySE(VTCretsim.long, measurevar = "similarity", groupvars = c("RewardType", "AgeGroup"))
```

## ERS

0. Quadratic age model is best-fitting
1. Main effect of age (p < 0.01), regardless of controlling for voxel number or removing 1 run subs

```{r analyzeVTCERS, echo = FALSE}
# Z-score age and voxel number and add age squared
VTCers.long$ageScaled <- scale(VTCers.long$ExactAge) # Scale age
VTCers.long$ageScaledsq <- (VTCers.long$ageScaled)^2
VTCers.long$goldencvoxnumScaled <- scale(VTCers.long$goldencvoxnum) # Scale voxel number

# Make high reward category into a factor
VTCers.long$HighRewardStim <- as.factor(VTCers.long$HighRewardStim)
VTCers.long$RewardType <- as.factor(VTCers.long$RewardType)

# Find best-fitting age model
VTCersd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCers.long)
VTCersd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCers.long)
anova(VTCersd1modelagelin, VTCersd1modelagesq) # agesq preferred

# Find viable rfx structure
# VTCersd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCers.long) # unidentifiable
VTCersd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCers.long)

# Model stats
Anova(VTCersd1modelnoslope, type = "III")

# Sensitivity analysis - control for voxel number, same pattern of results as above
VTCersd1modelnoslopevoxnum <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + goldencvoxnumScaled + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCers.long)
Anova(VTCersd1modelnoslopevoxnum, type = "III")

# Sensitivity analysis - remove subs with only 1 run
singlerunsubs <- VTCRSAdata$subid[rowSums(is.na(VTCRSAdata)) > 0]
singlerunsubs <- as.vector(singlerunsubs)
VTCers.long.tworunsonly <- VTCers.long[!VTCers.long$subid %in% singlerunsubs, ]

# Same pattern of results as above
VTCersd1modelnoslopetworuns <- VTCersd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCers.long.tworunsonly)
Anova(VTCersd1modelnoslopetworuns, type = "III")

# Plot
ggplot(VTCers.long, aes(y = similarity, x = ExactAge, colour = RewardType, group = RewardType)) +
  geom_point(size = 3) + # make each subject a different color dot
  stat_smooth(method = "glm",formula = y~poly(x, 2), fullrange = TRUE, aes(fill = RewardType), size = 3) + # add line of best fit
  xlab("Age") + # x axis label
  ylab("Encoding-Retrieval Similarity") + # y axis label
  # ggtitle("All trials") +
  scale_colour_manual(values = c("gold", "snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold", "snow4"), guide = "none") +
  geom_line(aes(group = subid), color = "grey", size = .1) +
  # ylim(0, 0.602) +
  rsa_theme
ggsave('figures/ERS.png', width = 12, height = 8)

# Compute average for two-lines test
# VTCRSAdata$avgERS <- (VTCRSAdata$highrewardERS + VTCRSAdata$lowrewardERS) / 2
# twolines(avgERS~ExactAge, graph = 1, link = "gaussian",data = VTCRSAdata)
```

##  Encoding similarity

0. Linear age model is best-fitting
1. Main effects of reward level (p < 0.001) and age (p < 0.05), regardless of controlling for voxel number or removing 1 run subs

```{r analyzeVTCEncodingSim, echo = FALSE, warning = FALSE, message = FALSE}
# Z-score age and voxel number and add age squared
VTCencsim.long$ageScaled <- scale(VTCencsim.long$ExactAge) # Scale age
VTCencsim.long$ageScaledsq <- (VTCencsim.long$ageScaled)^2
VTCencsim.long$goldencvoxnumScaled <- scale(VTCencsim.long$goldencvoxnum) # Scale voxel number

# Make high reward category into a factor
VTCencsim.long$HighRewardStim <- as.factor(VTCencsim.long$HighRewardStim)
VTCencsim.long$RewardType <- as.factor(VTCencsim.long$RewardType)

# Find best-fitting age model
VTCencsimd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCencsim.long)
VTCencsimd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCencsim.long)
anova(VTCencsimd1modelagelin, VTCencsimd1modelagesq) # agelin preferred

# Find viable rfx structure
# VTCencsimd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCencsim.long) # unidentifiable
VTCencsimd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCencsim.long)

# Model stats
Anova(VTCencsimd1modelnoslope, type = "III")

# Sensitivity analysis - control for voxel number, same pattern of results as above
VTCencsimd1modelnoslopevoxnum <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + goldencvoxnumScaled + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCencsim.long)
Anova(VTCencsimd1modelnoslopevoxnum, type = "III")

# Sensitivity analysis - remove subs with only 1 run
VTCencsim.long.tworunsonly <- VTCencsim.long[!VTCencsim.long$subid %in% singlerunsubs, ]

# Same pattern of results as above
VTCencsimd1modelnoslopetworuns <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCencsim.long.tworunsonly)
Anova(VTCencsimd1modelnoslopetworuns, type = "III")

# Plot
ggplot(VTCencsim.long, aes(y = similarity, x = ExactAge, colour = RewardType, group = RewardType)) +
  geom_point(size = 3) + # make each subject a different color dot
  stat_smooth(method = "lm", formula = y~x, fullrange = TRUE, aes(fill = RewardType), size = 3) + # add line of best fit
  xlab("Age") + # x axis label
  ylab("Encoding Similarity") + # y axis label
  # ggtitle("All trials") +
  scale_colour_manual(values = c("gold", "snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold", "snow4"), guide = "none") +
  geom_line(aes(group = subid), color = "grey", size = .1) +
  # ylim(0, 0.602) +
  rsa_theme
ggsave('figures/enc_sim.png', width = 12, height = 8)
```

## Retrieval similarity

0. Linear age model is best-fitting
1. No effects

```{r analyzeVTCRetrievalSim, echo = FALSE, warning = FALSE, message = FALSE}
# Z-score age and voxel number and add age squared
VTCretsim.long$ageScaled <- scale(VTCretsim.long$ExactAge) # Scale age
VTCretsim.long$ageScaledsq <- (VTCretsim.long$ageScaled)^2
VTCretsim.long$goldencvoxnumScaled <- scale(VTCretsim.long$goldencvoxnum) # Scale voxel number

# Make high reward category into a factor
VTCretsim.long$HighRewardStim <- as.factor(VTCretsim.long$HighRewardStim)
VTCretsim.long$RewardType <- as.factor(VTCretsim.long$RewardType)

# Find best-fitting age model
VTCretsimd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCretsim.long)
VTCretsimd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML = FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), data = VTCretsim.long)
anova(VTCretsimd1modelagelin, VTCretsimd1modelagesq) # agelin preferred

# Find viable rfx structure
# VTCretsimd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCretsim.long) # unidentifiable
VTCretsimd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = VTCretsim.long)

# Model stats
Anova(VTCretsimd1modelnoslope, type = "III")

# Plot
ggplot(VTCretsim.long, aes(y = similarity, x = ExactAge, colour = RewardType, group = RewardType)) + 
  geom_point(size = 3) + # make each subject a different color dot
  stat_smooth(method = "lm",formula = y~x, fullrange = TRUE, aes(fill = RewardType), size = 3) + # add line of best fit
  xlab("Age") + # x axis label
  ylab("Retrieval Similarity") + # y axis label
  # ggtitle("All trials") +
  scale_colour_manual(values = c("gold", "snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold", "snow4"), guide = "none") +
  geom_line(aes(group = subid), color = "grey", size = .1) +
  # ylim(0, 0.602) +
  rsa_theme
```

# Anterior Hippocampus Pattern Similarity LEFT OFF HERE

```{r wrangleDataAntHippPatternSim, echo = FALSE}

#Read in ERS data
anthippRSAdata = read.csv("data/RSAdata_antHIPP.csv")

anthippRSAdata$subid = as.factor(anthippRSAdata$subid)

#merge
anthippRSAdata <- full_join(anthippRSAdata, demog, by = "subid")

anthippRSAdata$HighRewardStim = ifelse(as.numeric(as.character(anthippRSAdata$subid)) %% 2 == 0, "High Reward Cat - Face","High Reward Cat - Place")

anthippERSvoxels = read.csv("data/RSAdfQAantHIPP.csv")

anthippERSvoxels$subID = gsub("sub-","",anthippERSvoxels$subID)
anthippERSvoxels$subid = as.factor(anthippERSvoxels$subID)

#merge
anthippRSAdata <- full_join(anthippRSAdata, anthippERSvoxels, by = "subid")


#anthipp ERS
anthippers.long = melt(anthippRSAdata,
                          id.vars=c("subid","HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldencvoxnum"),
                          measure.vars= c("highrewardERS", "lowrewardERS"),
                          variable.name= "ERScond")
names(anthippers.long)[names(anthippers.long)=="value"] <- "similarity"
findRew <- "(high|low)"
anthippers.long <- transform(anthippers.long, RewardType=stringr::str_extract(ERScond,findRew))

anthippers.longwstat = summarySE(anthippers.long, measurevar= "similarity", groupvars=c("RewardType","AgeGroup"))


#anthipp enc sim
anthippencsim.long = melt(anthippRSAdata,
                          id.vars=c("subid","HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldencvoxnum"),
                          measure.vars= c("highrewardencsim", "lowrewardencsim"),
                          variable.name= "encsimcond")
names(anthippencsim.long)[names(anthippencsim.long)=="value"] <- "similarity"
findRew <- "(high|low)"
anthippencsim.long <- transform(anthippencsim.long, RewardType=stringr::str_extract(encsimcond,findRew))

anthippencsim.longwstat = summarySE(anthippencsim.long, measurevar= "similarity", groupvars=c("RewardType","AgeGroup"))

#anthipp ret sim
anthippretsim.long = melt(anthippRSAdata,
                          id.vars=c("subid","HighRewardStim", "AgeGroup", "ExactAge", "Gender", "goldretvoxnum"),
                          measure.vars= c("highrewardretsim", "lowrewardretsim"),
                          variable.name= "retsimcond")
names(anthippretsim.long)[names(anthippretsim.long)=="value"] <- "similarity"
findRew <- "(high|low)"
anthippretsim.long <- transform(anthippretsim.long, RewardType=stringr::str_extract(retsimcond,findRew))

anthippretsim.longwstat = summarySE(anthippretsim.long, measurevar= "similarity", groupvars=c("RewardType","AgeGroup"))
```

## ERS

```{r analyzeAntHippERS, echo = FALSE}
#anthipp ERS stats

#z-score age and add age squared
anthippers.long$ageScaled <- scale(anthippers.long$ExactAge) #scale age
anthippers.long$ageScaledsq <- (anthippers.long$ageScaled)^2
anthippers.long$goldencvoxnumScaled <- scale(anthippers.long$goldencvoxnum) #scale voxel number

#make reward stimulus category into a factor
anthippers.long$HighRewardStim <- as.factor(anthippers.long$HighRewardStim)
anthippers.long$RewardType <- as.factor(anthippers.long$RewardType)

#first fit age models and determine whether age linear or squared provides better fit
anthippersd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippers.long)

anthippersd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippers.long)

anova(anthippersd1modelagelin,anthippersd1modelagesq) #age lin preferred

#anthippersd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippers.long) #unidentifiable

anthippersd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippers.long)

Anova(anthippersd1modelnoslope, type="III")


#control for voxnum in ROI - same pattern
anthippersd1modelnoslopevoxcontrol <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + goldencvoxnumScaled + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippers.long)

Anova(anthippersd1modelnoslopevoxcontrol, type="III")


#remove subs with only 1 run - same pattern
singlerunsubs <- anthippRSAdata$subid[rowSums(is.na(anthippRSAdata)) > 0]
singlerunsubs <- as.vector(singlerunsubs)
anthippers.long.tworunsonly <- anthippers.long[!anthippers.long$subid %in% singlerunsubs, ]

anthippersd1modelnoslopetworuns <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippers.long.tworunsonly)

Anova(anthippersd1modelnoslopetworuns, type="III")



ggplot(anthippers.long, aes(y = similarity, x = ExactAge, colour=RewardType, group=RewardType)) + #define data; x & y variables
  geom_point(size=3) + #make each subject a different color dot
  stat_smooth(method="lm", formula=y~x, aes(fill=RewardType), size=3) + #add line of best fit
  xlab("Age") + #x axis label
  ylab("Encoding-Retrieval Similarity") + #y axis label
  scale_colour_manual(values = c("gold","snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold","snow4"), guide = "none") +
  geom_line(aes(group=subid), color="grey", size=.1) +
 # ylim(0, 0.602) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        legend.position="bottom",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))
```

## Encoding similarity

```{r analyzeAntHippEncodingSim, echo = FALSE}
#anthipp enc sim stats

#z-score age and add age squared
anthippencsim.long$ageScaled <- scale(anthippencsim.long$ExactAge) #scale age
anthippencsim.long$ageScaledsq <- (anthippencsim.long$ageScaled)^2
anthippencsim.long$goldencvoxnumScaled <- scale(anthippencsim.long$goldencvoxnum) #scale voxel number

#make reward stimulus category into a factor
anthippencsim.long$HighRewardStim <- as.factor(anthippencsim.long$HighRewardStim)
anthippencsim.long$RewardType <- as.factor(anthippencsim.long$RewardType)

#first fit age models and determine whether age linear or squared provides better fit
anthippencsimd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippencsim.long)

anthippencsimd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippencsim.long)

anova(anthippencsimd1modelagelin,anthippencsimd1modelagesq) #age lin preferred

#anthippencsimd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippencsim.long) #unidentifiable

anthippencsimd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippencsim.long)

Anova(anthippencsimd1modelnoslope, type="III")

#control for voxels in mask - same pattern
anthippencsimd1modelnoslopevoxcontrol <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + goldencvoxnumScaled + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippencsim.long)

Anova(anthippencsimd1modelnoslopevoxcontrol, type="III")


ggplot(anthippencsim.long, aes(y = similarity, x = ExactAge, colour=RewardType, group=RewardType)) + #define data; x & y variables
  geom_point(size=3) + #make each subject a different color dot
  stat_smooth(method="lm", formula=y~x, aes(fill=RewardType), size=3) + #add line of best fit
  xlab("Age") + #x axis label
  ylab("Encoding Similarity") + #y axis label
  scale_colour_manual(values = c("gold","snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold","snow4"), guide = "none") +
  geom_line(aes(group=subid), color="grey", size=.1) +
 # ylim(0, 0.602) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        legend.position="bottom",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))
```

## Retrieval similarity

```{r analyzeAntHippRetrievalSim, echo = FALSE}
#anthipp enc sim stats

#z-score age and add age squared
anthippretsim.long$ageScaled <- scale(anthippretsim.long$ExactAge) #scale age
anthippretsim.long$ageScaledsq <- (anthippretsim.long$ageScaled)^2
anthippretsim.long$goldretvoxnumScaled <- scale(anthippretsim.long$goldretvoxnum) #scale voxel number

#make reward stimulus category into a factor
anthippretsim.long$HighRewardStim <- as.factor(anthippretsim.long$HighRewardStim)
anthippretsim.long$RewardType <- as.factor(anthippretsim.long$RewardType)

#first fit age models and determine whether age linear or squared provides better fit
anthippretsimd1modelagelin <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippretsim.long)

anthippretsimd1modelagesq <- lmer(similarity ~ RewardType * ageScaled + RewardType * ageScaledsq + HighRewardStim + (1|subid), REML=FALSE, control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), data = anthippretsim.long)

anova(anthippretsimd1modelagelin,anthippretsimd1modelagesq) #age lin preferred

#anthippretsimd1modelfullrfx <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (RewardType||subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippretsim.long) #unidentifiable

anthippretsimd1modelnoslope <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + (1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippretsim.long)

Anova(anthippretsimd1modelnoslope, type="III")

#control for voxels in mask - same pattern
anthippretsimd1modelnoslopevoxcontrol <- lmer(similarity ~ RewardType * ageScaled + HighRewardStim + goldretvoxnumScaled +(1|subid), control = lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = anthippretsim.long)

Anova(anthippretsimd1modelnoslopevoxcontrol, type="III")


ggplot(anthippretsim.long, aes(y = similarity, x = ExactAge, colour=RewardType, group=RewardType)) + #define data; x & y variables
  geom_point(size=3) + #make each subject a different color dot
  stat_smooth(method="lm", formula=y~x, aes(fill=RewardType), size=3) + #add line of best fit
  xlab("Age") + #x axis label
  ylab("Retrieval Similarity") + #y axis label
  scale_colour_manual(values = c("gold","snow4"), name = "Reward Level") +
  scale_fill_manual(values = c("gold","snow4"), guide = "none") +
  geom_line(aes(group=subid), color="grey", size=.1) +
 # ylim(0, 0.602) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        legend.position="bottom",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

```

# Trialwise VTC ERS

```{r trialwiseVTC, echo = FALSE, results = "hide"}

#trial VTC ERS
trialwiseVTCERS = read.csv("data/trialwiseERS_VTC_wmemoryday2.csv")
trialwiseVTCERS$subid <- as.factor(trialwiseVTCERS$subid)

#merge
trialwiseVTCERSwdemog <- full_join(trialwiseVTCERS, demog, by = "subid")

#z-score age and add age squared
trialwiseVTCERSwdemog$ageScaled <- scale(trialwiseVTCERSwdemog$ExactAge) #scale age
trialwiseVTCERSwdemog$ageScaledsq <- (trialwiseVTCERSwdemog$ageScaled)^2
trialwiseVTCERSwdemog$ERSZ <- scale(trialwiseVTCERSwdemog$ERS) #scale age

#make character variables factors
trialwiseVTCERSwdemog$HighRewardStim = ifelse(as.numeric(as.character(trialwiseVTCERSwdemog$subid)) %% 2 == 0, "High Reward Cat - Face","High Reward Cat - Place")
trialwiseVTCERSwdemog$HighRewardStim <- as.factor(trialwiseVTCERSwdemog$HighRewardStim)
trialwiseVTCERSwdemog$RewardType <- as.factor(trialwiseVTCERSwdemog$RewardType)



VTCERStrialwiseacc <- glmer(memory ~ ERSZ + RewardType + ageScaled + HighRewardStim + (RewardType|subid), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = trialwiseVTCERSwdemog)

Anova(VTCERStrialwiseacc, type="III")

VTCERStrialwiseplotting <- glmer(memory ~ ERS + RewardType + ageScaled + HighRewardStim + (RewardType|subid), family=binomial, control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e6)), contrasts = list(RewardType = "contr.sum", HighRewardStim = "contr.sum"), data = trialwiseVTCERSwdemog)

Anova(VTCERStrialwiseplotting, type="III")

plot_model(VTCERStrialwiseplotting, type = "pred", terms = c("ERS [all]"), title="", line.size=2, colors="blue") +
    xlab("VTC Encoding-Retrieval Similarity") + #x axis label
  ylab("Specific Source Memory Day 2 \n Predicted Probability") +
  xlim(-0.2,0.6) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

# Brain-Behavior & Brain-Brain Relations

```{r relations, echo = FALSE}
#merge data and demog dfs
anthippRSAdatawbehav <- full_join(anthippRSAdata, behavdata, by = "subid")

anthippRSAdatawbehav$HighRewardStim <- as.factor(anthippRSAdatawbehav$HighRewardStim.x)

original_cols <- colnames(VTCRSAdata)
colnames(VTCRSAdata) <- paste("VTC" ,original_cols,sep=".")
names(VTCRSAdata)[names(VTCRSAdata) == 'VTC.subid'] <- 'subid'

anthippRSAdatawbehav <- full_join(anthippRSAdatawbehav, VTCRSAdata, by = "subid")

#load and merge encoding activation df
encactiv = read.csv("data/encodingactivation.csv")
encactiv$subid <- as.factor(encactiv$subid)


anthippRSAdatawbehav <- full_join(anthippRSAdatawbehav, encactiv, by = "subid")

#compute variables of interest
anthippRSAdatawbehav$highvlowERS <- (anthippRSAdatawbehav$highrewardERS - anthippRSAdatawbehav$lowrewardERS)

anthippRSAdatawbehav$highvlowERSabs <- abs(anthippRSAdatawbehav$highvlowERS)

anthippRSAdatawbehav$highvlowspecificmemd2 <- ((anthippRSAdatawbehav$HighRewAssocRetrievedHitDay2 + anthippRSAdatawbehav$HighRewAssocHitDay2)/2) - ((anthippRSAdatawbehav$LowRewAssocRetrievedHitDay2 + anthippRSAdatawbehav$LowRewAssocHitDay2)/2)

anthippRSAdatawbehav$VTC.highvlowencsim <- anthippRSAdatawbehav$VTC.highrewardencsim - anthippRSAdatawbehav$VTC.lowrewardencsim


#remove incomplete cases, z-score continuous predictors
anthippRSAdatawbehavfullruns <- anthippRSAdatawbehav[!is.na(anthippRSAdatawbehav$highrewardencsim),]


anthippRSAdatawbehavfullruns$ageScaled <- scale(anthippRSAdatawbehavfullruns$ExactAge.x) #scale age
anthippRSAdatawbehavfullruns$ageScaledsq <- (anthippRSAdatawbehavfullruns$ageScaled)^2 
 
anthippRSAdatawbehavfullruns$ageScaled <- as.numeric(anthippRSAdatawbehavfullruns$ageScaled)
anthippRSAdatawbehavfullruns$ageScaledsq <- as.numeric(anthippRSAdatawbehavfullruns$ageScaledsq)

anthippRSAdatawbehavfullruns$VTC.highvlowencsimZ <- scale(anthippRSAdatawbehavfullruns$VTC.highvlowencsim)
anthippRSAdatawbehavfullruns$highvlowERSabsZ <- scale(anthippRSAdatawbehavfullruns$highvlowERSabs)


#reward-sensitive ERS measure + memory regression + plots

summary(lm(highvlowspecificmemd2 ~ highvlowERSabs + VTC.highvlowencsim + ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns)) #hipp abs sig and VTC enc marginal (same results w Zsscored brain vars)

highvlowmemERSsim <- lm(highvlowspecificmemd2 ~ highvlowERSabs + VTC.highvlowencsim + ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns)

#plot_model(highvlowmemERSsim, type = "pred", terms = c("highvlowERSabs"),  show.data = TRUE, title = "", line.size=2) +
ggplot(anthippRSAdatawbehavfullruns, aes(y = highvlowspecificmemd2, x = highvlowERSabs)) + #define data; x & y variables
 geom_point(size=3, color="#73A291") + 
  geom_smooth(method=lm, size=2, color="#73A291", fill="#73A291") + 
      xlab("|High - Low Reward Hippocampal ERS|") + #x axis label
  ylab("High - Low Reward Memory") +
  xlim(0,0.08) +
  ylim(-0.3,0.4) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

  
#plot_model(highvlowmemERSsim, type = "pred", terms = c("VTC.highvlowencsim"),  show.data = TRUE, title = "", line.size = 2) +
ggplot(anthippRSAdatawbehavfullruns, aes(y = highvlowspecificmemd2, x = VTC.highvlowencsim)) + #define data; x & y variables
 geom_point(size=3, color="#388697") + 
  geom_smooth(method=lm, size=2, color="#388697", fill="#388697") + 
      xlab("High - Low Reward VTC Enc Similarity") + #x axis label
  ylab("High - Low Reward Memory") +
   xlim(-0.065,0.085) +
    ylim(-0.3,0.4) +
  #xlim(0,0.08) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))
  

#anthipp ERS + VTA regression + plots
anthippRSAdatawbehavfullruns$VTAZ <- scale(anthippRSAdatawbehavfullruns$VTA)


summary(lm(highvlowERS ~ VTA * ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns)) 

anthippERSVTAenc <- lm(highvlowERS ~ VTA * ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns) #same effect if VTA z-scored

#plot_model(anthippERSVTAenc, type = "pred", terms = c("VTA"),  show.data = TRUE, title = "", line.size=2) +
ggplot(anthippRSAdatawbehavfullruns, aes(y = highvlowERS, x = VTA)) + #define data; x & y variables
 geom_point(size=3, color="#BBBE64") + 
  geom_smooth(method=lm, size=2, color="#BBBE64", fill="#BBBE64") + 
      xlab("VTA High > Low Reward Enc Activation") + #x axis label
  ylab("High - Low Reward Hippocampal ERS") +
  #xlim(0,0.08) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

 
#VTC enc sim + dlPFC regression + plots
anthippRSAdatawbehavfullruns$dlPFCZ <- scale(anthippRSAdatawbehavfullruns$dlPFC)

summary(lm(VTC.highvlowencsim ~ dlPFC * ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns)) #same effect if dlPFC z-scored
VTCERSdlPFCenc <- lm(VTC.highvlowencsim ~ dlPFC * ageScaled + HighRewardStim, data = anthippRSAdatawbehavfullruns)

#plot_model(VTCERSdlPFCenc, type = "pred", terms = c("dlPFC"),  show.data = TRUE, title = "", line.size=2)+
ggplot(anthippRSAdatawbehavfullruns, aes(y = VTC.highvlowencsim, x = dlPFC)) + #define data; x & y variables
 geom_point(size=3, color="#293F14") + 
  geom_smooth(method=lm, size=2, color="#293F14", fill="#293F14") + 
      xlab("dlPFC High > Low Reward Enc Activation") + #x axis label
  ylab("High - Low Reward VTC Enc Similarity") +
  #xlim(0,0.08) +
  theme(title= element_text(size=26, vjust=2, face="bold"), #use these settings for titles unless otherwise specified
        axis.title.x= element_text(size=26),
        axis.title.y= element_text(size=26, vjust=1.5),
        axis.text.x= element_text(size=24, colour="black", vjust=0.6),
        axis.text.y= element_text(size=24, colour="black"),
        legend.title= element_text(size=24), #no legend, but just in case you need one
        legend.text= element_text(size=24),
        #legend.position="none",
        strip.text = element_text(size=24, face="bold"), #text in strip headings
        panel.grid.major = element_blank(), #take out grid marks
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))


#are encoding measures trading off?
summary(lm(dlPFC ~ VTA, data = anthippRSAdatawbehavfullruns))
encact <- lm(dlPFC ~ VTA, data = anthippRSAdatawbehavfullruns)

plot_model(encact, type = "pred", terms = c("VTA"),  show.data = TRUE, title = "", line.size=2)

```